The \dealii Library, Version 9.0

### 2018-05-09 9.0/paper.tex
Add note on adding notes for new tutorial programs.

This release does not contain any new tutorial programs, though
several have been updated extensively for the changes to the manifold
handling as well as to adjust for current functionality and coding styles
compared to what that was available when the programs were first written.

>>>>

\marginpar{LH, MK, and others: Please add summaries of the new tutorial programs.}
